---
title: "Qualitative analysis of exclusion patterns (keywords)"
author: "Marcos Baez"
date: "8/21/2018"
output: 
  html_document:
        toc: true
        toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

```{r echo=FALSE, message=FALSE, results='hide'}
file_include = commandArgs(TRUE)[1]
source("./screening-keywords.R")
```
The analysis is based on the file **`r commandArgs(TRUE)[1]`**.

A total of `r length(dj1$id)` judgments were collected from 
`r length(unique(dj1$X_worker_id))` workers on  `r length(unique(dj1$X_unit_id))` papers 
(`r length(unique(dj1$X_unit_id[dj1$X_golden == "TRUE"]))` of which were "golden"
or labeled items). After removing non valid contributions, we ended up with `r length(djv$id)` valid judgements. 


```{r message=FALSE, echo=FALSE, fig.height=4}
pdist
```

## Patterns
A total of `r length(djv$id)` judgements with valid patterns were identified
from the `r length(dj1$id)` collected. We considered invalid those patterns 
coming from contributions that did not follow the job instructions. 

```{r echo=FALSE, results='asis'}
print(xtable::xtable(dji, caption = "Reasons for invalid cases"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```

Below we illustrate the distribution of number of patterns in contributions. 
The range goes from 0-`r max(djv$nPatterns)`, with a median of `r median(djv$nPatterns)`.

```{r message=FALSE, echo=FALSE, fig.height=4}
ppat_hist
```

### Classifying patterns

We then performed a qualitative content analysis on the valid patterns to 
characterise to what concepts they refer to. The emerging coding scheme is 
listed below. 

| Category             | Example                                          |
|----------------------|--------------------------------------------------|
| Social               | The keywords provided were related to the concept of social interactions <br> e.g., *"Social isolation, social ties, social interaction"*|
| Technology           | The keywords provided were related to the concept of technology <br> e.g., *"Internet-of-Things, fall detection, energy efficiency, wearable device"*|
| Social & Technology  | The keywords provided were related to both technology and social interactions <br> e.g., *"benefits of social connections,Internet connectivity,social activity"*|
| Paper focus          | The keywords provided describe the focus of the paper <br> e.g., *"gaming console, health care and rehabilitation, activity group, social activity"*|
| Off topic            | The keywords provided do not relate to any of the aforementioned topics. <br> e.g., *"Questionnaire, longitudinal research"*|



In the chart below we show the count of unique patterns by category.

```{r message=FALSE, echo=FALSE, fig.height=4}
ppat_type
```


### Content analysis 
Looking deeper into the content of the patterns, we looked into the most popular 
keywords in abstracts marked as included and excluded. To this end, we took 
the unique pairs (paper, pattern) to avoid putting more weight into those abstracts with
more judgments, and computed a frequency table, removing from the sample those assessed by researcher
as low quality (more on the next section). The analysis was done separately 
for the set of papers marked as included and excluded.

Looking at the top 5 we can see the following (notice that the possible values for the keywords go from 1-`r max(unique(djv$X_unit_id))`).


```{r echo=FALSE, message=FALSE,warning=FALSE}
source("./text-analysis.R")

dpatterns1 <- djv[djv$in_out_radio == "yes" & djv$quality_reason != "bad", ]
dpatterns1 <- SplitKeywords(dpatterns1$X_unit_id, dpatterns1$reason_pattern)

# dpatterns1 <- melt(prop.table(table(dpatterns1$unitid, dpatterns1$pattern),1) * 2)
# dpatterns1 <- aggregate(ceiling(dpatterns1$value), by=list(Category=dpatterns1$Var2), FUN=sum)
# dpatterns1$x <- ceiling(dpatterns1$x)
# d_yes <- dpatterns1

dpatterns1 <- unique(dpatterns1)
d_yes <- data.frame(table(dpatterns1$pattern))

colnames(d_yes) <- c("word", "freq")
d_yes <- d_yes[order(d_yes$freq, decreasing = T), ]


dpatterns2 <- djv[djv$in_out_radio == "no" & djv$quality_reason != "bad", ]
dpatterns2 <- SplitKeywords(dpatterns2$X_unit_id, dpatterns2$reason_pattern)

# dpatterns2 <- melt(prop.table(table(dpatterns2$unitid, dpatterns2$pattern),1) * 2)
# dpatterns2 <- aggregate(ceiling(dpatterns2$value), by=list(Category=dpatterns2$Var2), FUN=sum)
# dpatterns2$x <- ceiling(dpatterns2$x)
# d_no <- dpatterns2

dpatterns2 <- unique(dpatterns2)
d_no <- data.frame(table(dpatterns2$pattern))

colnames(d_no) <- c("word", "freq")
d_no <- d_no[order(d_no$freq, decreasing = T), ]

rownames(d_yes) <- NULL
rownames(d_no) <- NULL

```


<style>
.container {
  display: flex; /* or inline-flex */
  width: 100%;
}
.container div {
  width : 50%;
  padding: 5px;
}
.container table, .container .row {
  width:100%;
}
.container table td {
  padding: 2px;
} 

.container img {
  width: 100%;
}

</style>


<div class="container">
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_yes, 20), caption = "Most popular keywords in patterns marked as included"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_no, 20), caption = "Most popular keywords in patterns marked as excluded"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
</div>



```{r echo=FALSE, message=FALSE,warning=FALSE}

dpatterns1 <- djv[djv$in_out_radio == "yes" & djv$quality_reason != "bad", ]
dpatterns1 <- SplitKeywords(dpatterns1$X_unit_id, dpatterns1$reason_pattern)
dpatterns1 <- unique(dpatterns1)

d_yes <- RenderCloud(dpatterns1$pattern, allowStemming = F)
colnames(d_yes) <- c("word", "freq")
d_yes <- d_yes[order(d_yes$freq, decreasing = T), ]


dpatterns2 <- djv[djv$in_out_radio == "no" & djv$quality_reason != "bad", ]
dpatterns2 <- SplitKeywords(dpatterns2$X_unit_id, dpatterns2$reason_pattern)
dpatterns2 <- unique(dpatterns2)

d_no <- RenderCloud(dpatterns2$pattern, allowStemming = F)
colnames(d_no) <- c("word", "freq")
d_no <- d_no[order(d_no$freq, decreasing = T), ]

rownames(d_yes) <- NULL
rownames(d_no) <- NULL

dx_yes <- d_yes [! d_yes$word %in% head(d_no$word,5), ]
dx_no <- d_no[! d_no$word %in% head(d_yes$word,5), ]

rownames(dx_yes) <- NULL
rownames(dx_no) <- NULL
```

After perform basic preprocessing to remove stopword and puctuations, as well
as considering every single term in the patterns we end up with the following
table and figure. 

<div class="container">
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_yes, 20), caption = "Most popular keywords in patterns marked as included"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_no, 20), caption = "Most popular keywords in patterns marked as excluded"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
</div>

<div class="container">
<div class="row">
```{r echo=FALSE, results='asis', warning=FALSE, fig.height=8, fig.width=8}
par(mfrow=c(1, 2),
    oma = c(0,0,0,0) + 0.1,
    mar = c(0,0,1,1) + 0.1)

set.seed(111)
wordcloud(
  words = dx_yes$word,
  freq = dx_yes$freq,
  min.freq = 1,
  max.words = 200,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
)
set.seed(111)
wordcloud(
  words = dx_no$word,
  freq = dx_no$freq,
  min.freq = 1,
  max.words = 200,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
)
par(mfrow=c(1, 1))
```
</div>
</div>


## Reasons

We performed content analysis using an emerging coding system to characterise
the reasons for including and excluding papers. The resuting categories can be 
seen in the table below:

| Category                      | Example                                    |
|-------------------------------|--------------------------------------------|
| **Summary**  <br> A summary of the paper (in the workers' words) was provided as reason.  |  *"This study approaches the ethnographic meaning of the coexistence of old an new technologies (radio and tv sets) in living rooms of elderly facilities in Kinshasa."*    |
| **Argument**  <br> Exclitic arguments for the decision are included.  |  *"The main focus in the study is the energy efficiency of the device. There is no social interaction."*    |
| **Copy & Paste**  <br> A copy of a portion of the abstract (or title) was provided as reason.  |  *"Older adults experiences of online social interactions: A phenomenological study."*    |
| **Induction**  <br> There is a inference made by the worker, not explicit in the abstract.  |  *"the paper is about social networking sites which usually involves online social interactions."*    |
| **Rephrase**  <br> Part of the abstract (mostly the pattern) is slightly rephrased as the reason.  |  *"The paper is about 'online' social interactions, especifically about SNS (social network sites) and how they can  improve older people's life satisfaction."*    |
| **Assertion**  <br> An assertion is made, with little or no supporting arguments.  |  *"the paper is about social online interactions, especificaclly about the health of social connections.."*    |
| **Generic**  <br> A generic or very general remark is made.  |  *"The paper talks about implementation of AI technology."*    |
| **Keywords**  <br> Keywords provided as the reason.  |  *"face to face"*, <br>  *"online"*   |
| **Off / incomplete**  <br> The reason has nothing to do with the filter and topic, or the argument is incomplete.  |  *"there is a study and an evaluation."* <br> *"The paper is not about 'online' social interactions, is about."*   |

In the chart below we can see the results from the classification of the patterns.

```{r message=FALSE, echo=FALSE, fig.height=4}
pres_type
```



## Quality of contributions
We also performed a qualitative assessment of the quality of the reasons and contributions 
provided by considering their content and context. We looked into the type of pattern 
provided (e.g., the effort put), how reasonable it was in light of the content of the 
abstract (e.g., did the decisions require much argumentation) and the final assessment 
(e.g., was the final assessment aligned with the reason and complexity of the abstract). 
We did not consider the contributor information in the assessment (e.g., all information
about the worker was hidden to the coder during the qualitative assessment). 


### Reason

A total of `r length(djv$id)` reasons were coded in an ordinal scale of (bad, poor, medium, good)
adding a fifth level (excellent) as there were some outstanding contributions that
deserved a closer look. We show the results divided by "golden" data and those with
unknown label. 

```{r message=FALSE, echo=FALSE, fig.height=4}
pres_quality + coord_flip()
```

### Patterns

We also looked at the quality of the patterns provided. A total of `r length(djv$id)` 
patterns were coded in an ordinal scale of (bad, poor, medium, good). 
The assessment is based on whether the keywords really support the judgement and 
reason provided by the worker, i.e., supports why the paper is related or not 
to social interactions and / or technology.

Below we show the results divided by "golden" data and those with unknown label. 

<div class="container">
<div class="row">
```{r message=FALSE, echo=FALSE, fig.height=4}
ppat_quality + coord_flip()
```
</div>
</div>

Consider task design in assessing the above results. 


### Contributors

The quality in this chart is measured by the quality of the 'reasons' provided, 
which also greatly influenced the quality of the patterns as mentioned before. 
<div class="container">
<div class="row">
```{r message=FALSE, echo=FALSE, fig.height=5}
pwork + coord_flip()
```
</div>
</div>



