---
title: "Qualitative analysis of exclusion patterns (sentences)"
author: "Marcos Baez"
date: "8/15/2018"
output: 
  html_document:
        toc: true
        toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Dataset

```{r echo=FALSE, message=FALSE, results='hide'}
file_include = commandArgs(TRUE)[1]
source("./screening-sentence.R")
```

The analysis is based on the file **`r commandArgs(TRUE)[1]`**.


A total of `r length(dj1$id)` judgments were collected from 
`r length(unique(dj1$X_worker_id))` workers on  `r length(unique(dj1$X_unit_id))` papers 
(`r length(unique(dj1$X_unit_id[dj1$X_golden == "TRUE"]))` of which were "golden"
or labeled items). After removing non valid contributions, we ended up with `r length(djv$id)` valid judgements. 

In the figure below we show the distribution of the number of judgements per 
paper. 


```{r message=FALSE, echo=FALSE, fig.height=4}
p4
```


## Patterns
A total of `r length(djv$id)` judgements with valid patterns were identified
from the `r length(dj1$id)` collected. We considered invalid those patterns with no 
match in the abstract. 

```{r echo=FALSE, results='asis'}
print(xtable::xtable(dji, caption = "Reasons for invalid cases"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```

### Classifying patterns

We then performed a qualitative content analysis on the valid patterns to 
characterise to which parts of an abstract they refer to. We took as coding scheme
the common parts of a typical abstract structure (see table below). Notice that
we qualitative analised the patterns instead of taking the raw
position of the matching pattern, as i) most abstracts were not structured, and 
therefore ii) the structure can change according to the writing style of the authors 
(e.g., some abstracts may start with the "Objective" while others with some general
"Background" information).

The coding scheme is listed below. To the list we added the category "Keyword" to indicate short patterns that not correspond to complete sentences. 

| Part of the abstract | Example                                          |
|----------------------|--------------------------------------------------|
| Background           | *Social isolation in urban areas is a societal challenge. It affects people of all ages but particularly elderly who struggle to maintain social ties into later-life. Interventions in social isolation primarily focus on elderly in clinical care, overlooking the existence of older adults who live independently*|
| Hypothesis           | *A novel security mechanism named as the traceable threshold attribute-based signcryption (TTABSC) can permits patients to be friends and make a proper tradeoff between privacy and traceability*|
| Objective            | *This study is part of a design-based research project aimed at designing a learning intervention for enabling Costa Rican older people to use information and communication technologies for cognitive activity and social interaction*|
| Proposal             | *we propose FamilyPal, an effective system for detecting family activities, which can help users establish good relationship with family members*|
| Proposal details     | *Specifically, FamilyPal firstly uses smartphones built-in sensors, such as GPS, accelerometer, microphone, gyroscope, and Wi-Fi to obtain the motion and location of users, the surrounding voice, etc.*|
| Methods              | *We use path analysis to test their relationships with attitude, perceived value and watching intention to understand the influential factors and channels that induce audiences to watch live-streaming events.*|
| Results              | *The empirical results show that SNS use improves older people's life satisfaction by reducing their loneliness and improving their self-efficacy. Social support alleviates the negative effect of loneliness and enhances the positive effect of self-efficacy on life satisfaction*|
| Keyword              | *83-item online survey*|


In the chart below we show the count of unique patterns by category.

```{r message=FALSE, echo=FALSE, fig.height=4}
p3
```


### Content analysis 
Looking deeper into the content of the patterns, we looked into the most popular 
keywords in abstracts marked as included and excluded. To this end, we took 
the unique patterns (to avoid putting more weight into those abstracts with
more judgments) and perform basic preprocessing to remove stopword and puctuations.
We then computed a frequency table for terms in the patterns belonging to 
included and excluded judgments, removing for the sample those assessed by researcher
as low quality (more on the next section). It is important to mention, however, 
that we did not consider the gold answer in this assessment, just the overall
quality of the pattern and reason provided.


Looking at the top 5 we can see:

```{r echo=FALSE, message=FALSE,warning=FALSE,results='hide'}
source("./text-analysis.R")

dpatterns1 <- djv[djv$in_out_radio == "yes" & djv$quality_reason != "bad", ]
dpatterns1 <- unique(str_replace_all(dpatterns1$reason_pattern, "[[:punct:]]", ""))  
d_yes <- RenderCloud(dpatterns1)

dpatterns2 <- djv[djv$in_out_radio == "no" & djv$quality_reason != "bad", ]
dpatterns2 <- unique(str_replace_all(dpatterns2$reason_pattern, "[[:punct:]]", ""))  
d_no <- RenderCloud(dpatterns2)

rownames(d_yes) <- NULL
rownames(d_no) <- NULL

dx_yes <- d_yes [! d_yes$word %in% head(d_no$word,5), ]
dx_no <- d_no[! d_no$word %in% head(d_yes$word,5), ]

rownames(dx_yes) <- NULL
rownames(dx_no) <- NULL

```

<style>
.container {
  display: flex; /* or inline-flex */
  width: 100%;
}
.container div {
  width : 50%;
  padding: 5px;
}
.container table, .container .row {
  width:100%;
}
.container table td {
  padding: 2px;
} 

.container img {
  width: 100%;
}

</style>

<div class="container">
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_yes, 5), caption = "Most popular keywords in patterns marked as included"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(d_no, 5), caption = "Most popular keywords in patterns marked as excluded"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
</div>

Below the term frequency and word clouds after removing the top 5 terms.

<div class="container">
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(dx_yes, 20), caption = "Most popular keywords in patterns marked as included"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
<div>
```{r echo=FALSE, results='asis'}
print(xtable::xtable(head(dx_no, 20), caption = "Most popular keywords in patterns marked as excluded"),
type = "html", html.table.attributes ="style='border=0;padding=2'")
```
</div>
</div>

<div class="container">
<div class="row">
```{r echo=FALSE, results='asis', warning=FALSE, fig.height=8, fig.width=8}
par(mfrow=c(1, 2),
    oma = c(0,0,0,0),
    mar = c(0,0,0,0))

set.seed(1234)
wordcloud(
  words = dx_yes$word,
  freq = dx_yes$freq,
  min.freq = 2,
  max.words = 200,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
)
wordcloud(
  words = dx_no$word,
  freq = dx_no$freq,
  min.freq = 2,
  max.words = 200,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
)
par(mfrow=c(1, 1))
```
</div>
</div>

## Reasons

We performed content analysis using an emerging coding system to characterise
the reasons for including and excluding papers. The resuting categories can be 
seen in the table below:

| Category                      | Example                                    |
|-------------------------------|--------------------------------------------|
| **Summary**  <br> A summary of the paper (in the workers' words) was provided as reason.  |  *"This study approaches the ethnographic meaning of the coexistence of old an new technologies (radio and tv sets) in living rooms of elderly facilities in Kinshasa."*    |
| **Argument**  <br> Exclitic arguments for the decision are included.  |  *"The main focus in the study is the energy efficiency of the device. There is no social interaction."*    |
| **Copy & Paste**  <br> A copy of a portion of the abstract (or title) was provided as reason.  |  *"Older adults experiences of online social interactions: A phenomenological study."*    |
| **Induction**  <br> There is a inference made by the worker, not explicit in the abstract.  |  *"the paper is about social networking sites which usually involves online social interactions."*    |
| **Rephrase**  <br> Part of the abstract (mostly the pattern) is slightly rephrased as the reason.  |  *"The paper is about 'online' social interactions, especifically about SNS (social network sites) and how they can  improve older people's life satisfaction."*    |
| **Assertion**  <br> An assertion is made, with little or no supporting arguments.  |  *"the paper is about social online interactions, especificaclly about the health of social connections.."*    |
| **Generic**  <br> A generic or very general remark is made.  |  *"The paper talks about implementation of AI technology."*    |
| **Keywords**  <br> Keywords provided as the reason.  |  *"face to face"*, <br>  *"online"*   |
| **Off / incomplete**  <br> The reason has nothing to do with the filter and topic, or the argument is incomplete.  |  *"there is a study and an evaluation."* <br> *"The paper is not about 'online' social interactions, is about."*   |

In the chart below we can see the results from the classification of the patterns.

```{r message=FALSE, echo=FALSE, fig.height=4}
p2
```



## Quality of contributions
We also performed a qualitative assessment of the quality of the reasons and contributions 
provided by considering their content and context. We looked into the type of pattern 
provided (e.g., the effort put), how reasonable it was in light of the content of the 
abstract (e.g., did the decisions require much argumentation) and the final assessment 
(e.g., was the final assessment aligned with the reason and complexity of the abstract). 
We did not consider the contributor information in the assessment (e.g., all information
about the worker was hidden to the coder during the qualitative assessment). 

A total of `r length(djv$id)` reasons were coded in an ordinal scale of (bad, medium, good)
adding a fourth level (excellent) as there were some outstanding contributions that
deserved a closer look. We show the results divided by "golden" data and those with
unknown label. 

<div class="container">
  <div class="row">
```{r message=FALSE, echo=FALSE, fig.height=4}
p1 + coord_flip()
```
  </div>
</div>

Analysing quality of contributions by worker, we can see the following:

<div class="container">
  <div class="row">
  ```{r message=FALSE, echo=FALSE, fig.height=5}
  pwork + coord_flip()
  ```
  </div>
</div>


